Covid-19 análise espaço-temporal.

### 2020-11-26 Notebooks/intr_results.rmd
Update intr_results.rmd

---
title: "Covid-19 análise espaço-temporal."
author: "Lucas Rabelo"
output:
  word_document:
    toc: no
    toc_depth: '6'
  pdf_document:
    toc: no
    toc_depth: '6'
    number_sections: no
    keep_tex: yes
    citation_package: natbib
    pandoc_args: --listings
    includes: null
geometry: margin=1in
fontsize: 12pt
linestretch: 1.5
documentclass: report
---

@@

![](men_local_deaths.png)
**Figura 22 -** Índice local de Moran do número mensal de mortes por habitantes.

>>>>

---
title: "Covid-19 análise espaço-temporal."
author: "Lucas Rabelo"
output:
  pdf_document:
    toc: no
    toc_depth: '6'
    number_sections: no
    keep_tex: yes
    citation_package: natbib
    pandoc_args: --listings
    includes: null
  word_document:
    toc: no
    toc_depth: '6'
geometry: margin=1in
fontsize: 12pt
linestretch: 1.5
documentclass: report
---

@@

![](local_moran_d.png)
**Figura 22 -** Índice local de Moran do número mensal de mortes por habitantes.
